Overview

### 2019-03-15 notebooks/general_info.Rmd
added functionality to translate between type systems. numbers up for a type system corresponding to Rs as it stands, next up will be rolling NULLs into all other types

>>>>

Let's see what happens if we change type systems!
```{r}
los_basic <- lapply(los, function(lof) {lapply(lof, function(df) {change_type_systems_df(df, type_map_T0_to_r)})})
```

Let's get some counts.
This is for a type system which is in direct correspondence with R's typeof.
```{r}
# argument counts
total_mono_type_basic <- apply_count_to_lopkg_c(los_basic, args_count_all_mono_type)
total_mono_all_basic <- apply_count_to_lopkg_c(los_basic, args_count_all_mono_all)
```

What if we roll NULL into every type?
